Visualising Life Satisfaction in Countries across Europe: Individual- and Multi-Level Evidence on Cultural and Pecuniary Factors

### 2019-01-30 LaTex/Paper_fulltext.tex
Manifesto first draft
cdbk.tex

\section{Introduction and Preliminary remarks}
Anecdotal evidence suggests that people spend a significant share of their lifetime working (for a casual calculation 
see: \citet{thompson_what_2016}). Moreover, people's work environment is changing constantly and especially today's 
discussion about the impact of digitalisation on the labour market requires to investigate how occupational factors shape 
people's life in general. Since work constitutes a considerable part of people’s life, satisfaction with one’s job and the
occupational environment must severely determine overall well-being. Drawing on the above-mentioned diversity of 
occupations, their respective circumstances and adaptation to the ‘digital revolution’, this assumption gains even more 
ground and relevance: \textit{If work changes, life changes.} \\
But which work-related factors contribute to a happy - or unhappy - life? Also, how does life satisfaction of the employed
vary across regions and countries? \\
Using data form the European Values Survey (EVS), we calculated multiple regression models to assess the causality of
work-related factors and well-being on the individual level. Moreover, multi-level analyses with regard to social capital and
macroeconomic as well as developmental indicators were performed to account for variation across regions and countries.

>>>>

\section{Introduction and Preliminary remarks}
Anecdotal evidence suggests that people spend a significant share of their lifetime working (for a casual calculation 
see: \citet{thompson_what_2016}). Moreover, people's work environment is changing constantly and especially today's 
discussion about the impact of digitalisation on the labour market requires to investigate how occupational factors shape 
people's life in general. Since work constitutes a considerable part of people’s life, satisfaction with one’s job and the
occupational environment must severely determine overall well-being. Drawing on the above-mentioned diversity of 
occupations, their respective circumstances and adaptation to the ‘digital revolution’, this assumption gains even more 
ground and relevance: \textit{If work changes, life changes.} \\
But which work-related factors contribute to a happy - or unhappy - life? Also, how does life satisfaction of the employed
vary across regions and countries? \\
Using data form the European Values Survey (EVS) and several other sources, we calculated multiple regression models to assess the causality of
work-related factors and well-being on the individual level. Moreover, multi-level analyses with regard to social capital and
macroeconomic as well as developmental indicators were performed to account for variation across regions and countries. 
%% Könntest du den Fokus ein wenig weg von Work und hin auf multilevel + pecuniary/ non-pecuiary setzen, für so viel Fokus haben wir nicht genug work-relatedness
\section{Motivational Manifesto}
In a time of widespread digitalisation for many aspects of modern society, 'datafication' and subsequent analysis of data has become ever more prevalent \cite{baack_datafication_2015, lycett_datafication:_2013}. Transparency of data sourcing, data access and methods employed in the course of this analysis is a chief concern of the 'Open Science' movement\cite{miguel_promoting_2014}. With more and more transparency, reproducibility of procedures is expected to increase and thus the quality of insights by replication and and improvements of methods through a 'wisdom of the (educated) crowd'. There have been extensive developments in the form of guidelines and protocols for researchers, universities and scientific journals that are aimed at promoting more transparency in the scientific process \cite{nosek_promoting_2015}. 
At the same time, large shares of the population lack the essential skills to participate in the whole process or perceive the barrier of entry in acquiring the necessary skills to do so, as unsurmountably high. The concept of 'Citizen Science' has thus emerged sitting at the edge of both science and education. Citizen science projects enlist non-scientiest members of the public to participate in the research (mainly in data collection), allowing to survey large amounts of data, while educating participants about the research topic \cite{shirk_public_2012}. Originally coming from environmental research this approach has already allowed researcher to survey wide ranges of locations and time periods and thus provides access to high-quality data that could quite impossibly be attained by professional research teams on their own \cite{bonney_citizen_2009}.

Conceptually, 'Open Science' and 'Citizen Science' are deeply intertwined as 'Citizen Science' needs to be as transparent and easily accessible as possible to be effective on a large scale and 'Open Science' needs to offer educational value and low entry barriers if it wants to gain attention and participation of a broader audience. We feel committed to the mission of these movements and have thus designed our project in order to advance it for the social sciences.
